---
title: "Logistic Regression Models with GEE for the Secondary Outcomes in the VQI FBVAR Dataset"
author: "Jennifer Ci, Thu Vu, Lily Hanyi Wang"
output: pdf_document
---

```{r library, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
library(tidyverse)
library(table1)
library(dplyr)
library(geepack)
library(gtsummary)
library(broom.mixed)
```

```{r setup wd}
## ------------- working directories for Lily ----------
wd_lily = '/Users/hanyiwang/Desktop/Comparative-analysis-of-treatments-of-CAA'
path_lily = c("../data/TEVAR_PROC.csv")

## ------------- working directories for Jenn ----------
wd_jenn = '/Users/jenniferci/Desktop/stlp new laptop/Capstone/Comparative-analysis-of-treatments-of-CAA-main'
path_jenn = c("TEVAR_PROC.csv")

## ------------- read data ----------
setwd(wd_lily)
TEVAR_PROC = read.csv(path_lily)

# setwd(wd_jenn)
# PROC = read.csv(path_jenn)

```

# Variables to adjust for

```{r fig.height=20, fig.width=20}
# ### ---------- Correlation matrix ---------
# library(corrplot)
# library(tidyverse)
# library(caret)
# library(ggcorrplot)
# 
# matrix <- PROC %>%
#     select_if(is.numeric) %>% subset(., select = -1)%>%
#     cor(.,use = "complete")
# 
# corrplot(matrix, method="number")
# 
# #select dataset that column are not numeric
# matrix <- PROC %>% select_if(negate(is.numeric))
#   
# # find out the variables
# lapply(matrix[,], unique)
# sapply(lapply(matrix, unique), length)
# 
# #select if more than one variable
# y<-matrix %>%select_if(function(col) length(unique(col))==2)
# 
# # Convert all columns to factor
# data3 <- as.data.frame(unclass(y),                     
#                        stringsAsFactors = TRUE)
# 
#  model.matrix(~0 +., data=data3) %>% 
#   cor(use="pairwise.complete.obs") %>%
#   ggcorrplot(show.diag = F, type="lower", lab=TRUE, lab_size=2)
# 
# str(y) 
```

*We used a correlation matrix to report the correlations between variables statistically. We also discussed with our collaborator on the choice of variables to adjust for. Here we did not report the correlation matrix.*


- cluster on `CENTERID` 

- adjust for `AGECAT`, `GENDER`, `PREOP_SMOKING`, `PRIOR_AORSURG`, `PRIOR_CHF`, `PREOP_DIALYSIS`

- adjust for `PATHOLOGY`, `extent`

*In the model, we merge groups for the  `extent`: merge "Juxtarenal AAA" with "Type 4 TAAA"; "Type 1 TAAA", "Type 2 TAAA", "Type 3 TAAA", with "Type 5 TAAA". Now `extent` is a binary variable, Juxtarenal or not.*

- categorical secondary outcomes: `POSTOP_CEREBROSX`, `POSTOP_SPINAL_ISCHEMIA`, `POSTOP_DIALYSIS`, `POSTOP_LOS`,  `POSTOP_COMPLICATIONS`, `POSTOP_LEGEMBO`, `POSTOP_RESPIRATORY`, `RETX_R_RTOR`, `BRANCH_POST`, `TOTAL_LOS`,`ICUSTAY`, `POSTOP_INTISCH`

*logistic regression with Generalized Estimating Equations for categorical secondary outcomes*

- continuous secondary outcomes: `POSTOP_PRBC` 

*linear regression with Generalized Estimating Equations for continuous secondary outcomes*

`POSTOP_GFR`


```{r}
## ------------- modify dataset ----------
TEVAR_PROC = TEVAR_PROC %>%
  mutate(extent = factor(extent,levels = c("Juxtarenal AAA","Type 1 TAAA","Type 2 TAAA","Type 3 TAAA","Type 4 TAAA","Type 5 TAAA"),labels = c('Juxtarenal','No','No','No','Juxtarenal','No'))) %>%
  
  mutate(TOTAL_LOS = case_when(TOTAL_LOS>7 ~ '>7',
                               TOTAL_LOS<=7 ~ '<=7')) %>%
  mutate(ICUSTAY = case_when(ICUSTAY>4 ~ '>4',
                             ICUSTAY<=4 ~ '<=4')) %>%
  mutate(POSTOP_LOS = case_when(POSTOP_LOS>7 ~ '>7',
                                POSTOP_LOS<=7 ~ '<=7')) %>%

  mutate(TOTAL_LOS = as.numeric(TOTAL_LOS != "<=7") ) %>%
  mutate(ICUSTAY = as.numeric(ICUSTAY != "<=4") ) %>%
  mutate(POSTOP_LOS = as.numeric(POSTOP_LOS != "<=7") ) %>%
  
  mutate(POSTOP_INTISCH = as.numeric(POSTOP_INTISCH == "Yes"))  %>%
  mutate(POSTOP_CEREBROSX = as.numeric(POSTOP_CEREBROSX == "Yes")) %>%
  mutate(POSTOP_SPINAL_ISCHEMIA = as.numeric(POSTOP_SPINAL_ISCHEMIA == "Yes")) %>%
  mutate(POSTOP_DIALYSIS = as.numeric(POSTOP_DIALYSIS == "Yes")) %>%
  mutate(POSTOP_COMPLICATIONS = as.numeric(POSTOP_COMPLICATIONS == "Yes")) %>%
  mutate(POSTOP_LEGEMBO = as.numeric(POSTOP_LEGEMBO == "Yes")) %>%
  mutate(POSTOP_RESPIRATORY = as.numeric(POSTOP_RESPIRATORY == "Yes")) %>%
  mutate(RETX_R_RTOR = as.numeric(RETX_R_RTOR == "Yes")) %>%
  mutate(BRANCH_POST = as.numeric(BRANCH_POST == "Yes"))

# remove missing values
TEVAR_PROC = subset(TEVAR_PROC, !is.na(extent))


## ------------- change class of variables ----------
names <- c('CENTERID','AGECAT', 'GENDER', 'PREOP_SMOKING', 'PRIOR_AORSURG', 'PRIOR_CHF', 'PREOP_DIALYSIS', 'PATHOLOGY', 'extent')
TEVAR_PROC[,names] <- lapply(TEVAR_PROC[,names] , factor)

```


## TOTAL_LOS: Length of stay in days between admission date and discharge date

```{r}
## ------------- Length of stay in days between admission date and discharge date ----------

#table(PROC$extent)
#PROCNM[is.na(PROCNM) | PROCNM=="Inf"] = NA
# repeated patients, need id, geeglm needs complete data, extent is not complete

## ------------- unadjusted ----------
LOS1<-geeglm(TOTAL_LOS~ PRESENTATION, data=TEVAR_PROC, family=binomial(link="logit"), id = CENTERID, corstr = "independence") 

t1<-LOS1 %>%
  tbl_regression(exponentiate=TRUE,
                 tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**TOTAL_LOS Length of Stay in days**")%>%as_flex_table()


## ------------- adjusted ----------
LOS2<-geeglm(TOTAL_LOS ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent
            , data=TEVAR_PROC, family=binomial(link="logit"),id = CENTERID, corstr = "independence") 
t2<-LOS2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**TOTAL_LOS Length of Stay in days**")%>%as_flex_table()


#the difference in mean number of sessions attended comparing treatment to control


#adjust<-c('PRESENTATION','AGECAT', 'GENDER', 'PREOP_SMOKING','PRIOR_AORSURG', 'PRIOR_CHF','PATHOLOGY','NUM_TREATED_BRANCHES')
#PROC %>%
#  tbl_uvregression(
#    y = TOTAL_LOS, 
#    x = PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+PATHOLOGY+NUM_TREATED_BRANCHES,
#    method = geepack::geeglm,
#    method.args = list(id = X+CENTERID, corstr = "independence"),
#    include = all_of(adjust)
#  ) %>%
#  as_kable()
```

\newpage
## ICUSTAY: ICU Stay

```{r}
## ------------- ICU Stay ----------

## ------------- unadjusted ----------
ICU1<-geeglm(ICUSTAY~ PRESENTATION, data=TEVAR_PROC, family=binomial(link="logit"), id = CENTERID, corstr = "independence") 

#summary(LOS2)
#summary(ICU1)

#ICU1<-geeglm(ICUSTAY ~ PRESENTATION, data=PROCNM,id = CENTERID, corstr = "independence") 
t1<-ICU1 %>%tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                           pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**ICU Stay**")%>%as_flex_table()

## ------------- adjusted ----------
ICU2<-geeglm(ICUSTAY ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent
            , family=binomial(link="logit"), data=TEVAR_PROC, id = CENTERID, corstr = "independence") 
t2<- ICU2 %>%tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                            pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**ICU Stay**")%>%as_flex_table()
```

\newpage
## POSTOP_PRBC: Transfusion # Units PRBC

```{r}
## -------------  Transfusion # Units PRBC ----------
## ------------- unadjusted ----------
POSTOP_PRBC1<-geeglm(POSTOP_PRBC ~ PRESENTATION, data=TEVAR_PROC,id = CENTERID, corstr = "independence") 
t1<-POSTOP_PRBC1 %>%tbl_regression(tidy_fun = broom.mixed::tidy,
                                   pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Transfusion # Units PRBC**")%>%as_flex_table()


## ------------- adjusted ----------
# POSTOP_PRBC2<-geeglm(POSTOP_PRBC ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent, data=TEVAR_PROC, id = CENTERID+X, corstr = "independence") 
# t2<- POSTOP_PRBC2 %>%tbl_regression(tidy_fun = broom.mixed::tidy,
#                                     pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
#   bold_p(t = 0.05)
# tbl_merge(tbls = list(t2),tab_spanner ="**Transfusion # Units PRBC**")%>%as_flex_table()


```

\newpage
## POSTOP_INTISCH: Post-op Intestinal Ischemia

```{r}
## ------------ Post-op Intestinal Ischemia  ----------
## ------------- unadjusted ----------
POSTOP_INTISCH1<-geeglm(POSTOP_INTISCH ~ PRESENTATION, family=binomial(link="logit"), data=TEVAR_PROC,id = CENTERID, corstr = "independence") 

t1<-POSTOP_INTISCH1 %>%tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                                      pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Intestinal Ischemia**")%>%as_flex_table()


## ------------- adjusted ----------
POSTOP_INTISCH2<-geeglm(POSTOP_INTISCH ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent
                       , data=TEVAR_PROC,family=binomial(link="logit"), id = CENTERID, corstr = "independence") 
t2<- POSTOP_INTISCH2 %>%tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                                       pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)
tbl_merge(tbls = list(t2),tab_spanner ="**Intestinal Ischemia**")%>%as_flex_table()

# model<-geeglm(as.numeric(POSTOP_DIALYSIS)~PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+PATHOLOGY+NUM_TREATED_BRANCHES, family=binomial(link = "logit"), data=PROC, id = X, corstr = "independence")

# model<-geeglm(outcome~predictor+confounder, family=binomial(link = "logit"), 
# data=na.omit(data), corstr='ar1', id=id, std.err="san.se")
# TOTAL_LOS
# ICUSTAY
# POSTOP_PRBC
# POSTOP_HIGHCREAT
# POSTOP_INTISCH
```


\newpage
## POSTOP_CEREBROSX: Post-op Cerebrovascular Stroke: 

Also account for `ARMNECK_ACCESS`

```{r}
## ------------- Post-op Cerebrovascular Stroke ----------
## ------------- unadjusted ----------
POSTOP_CEREBROSX1 = geeglm(POSTOP_CEREBROSX ~ PRESENTATION, 
                           data=TEVAR_PROC, family=binomial(link="logit"), 
                           id = CENTERID, corstr = "independence") 

t1 = POSTOP_CEREBROSX1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy, 
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Post-op Cerebrovascular Stroke**")%>%as_flex_table()

## ------------- adjusted ----------
POSTOP_CEREBROSX2 = geeglm(POSTOP_CEREBROSX ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+
                      PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent+ARMNECK_ACCESS, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = POSTOP_CEREBROSX2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Post-op Cerebrovascular Stroke**")%>%as_flex_table()
```


\newpage
## POSTOP_SPINAL_ISCHEMIA: Post-op Spinal Ischemia

Also account for `POSTOP_SPINALDRAIN` and `OCCLUDED_CELIAC`

```{r}
## ------------- Post-op Spinal Ischemia  ----------
## ------------- unadjusted ----------
POSTOP_SPINAL_ISCHEMIA1 = geeglm(POSTOP_SPINAL_ISCHEMIA ~ PRESENTATION, 
                                 data=TEVAR_PROC,family=binomial(link="logit"), 
                                 id = CENTERID, corstr = "independence") 

t1 = POSTOP_SPINAL_ISCHEMIA1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Post-op Spinal Ischemia**")%>%as_flex_table()

## ------------- adjusted ----------
POSTOP_SPINAL_ISCHEMIA2 = geeglm(POSTOP_SPINAL_ISCHEMIA ~ PRESENTATION+AGECAT+GENDER+
                                   PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+
                                   PREOP_DIALYSIS+PATHOLOGY+extent+
                                   POSTOP_SPINALDRAIN+OCCLUDED_CELIAC, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = POSTOP_SPINAL_ISCHEMIA2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Post-op Spinal Ischemia**")%>%as_flex_table()



```



\newpage
## POSTOP_LOS: Length of stay in days between surgery date and discharge date

```{r}
## ------------ Length of stay in days between surgery date and discharge date  ----------
## ------------- unadjusted ----------
POSTOP_LOS1 = geeglm(POSTOP_LOS~ PRESENTATION, 
                     data=TEVAR_PROC, family=binomial(link="logit"), 
                     id = CENTERID, corstr = "independence") 
# summary(POSTOP_LOS1)

t1 = POSTOP_LOS1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Length of stay in days between surgery date and discharge date**")%>%as_flex_table()

## ------------- adjusted ----------
POSTOP_LOS2 = geeglm(POSTOP_LOS ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+
                      PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = POSTOP_LOS2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Length of stay in days between surgery date and discharge date**")%>%as_flex_table()
```

\newpage
## POSTOP_COMPLICATIONS: Any Complications Post-op

```{r}
## ------------ Any Complications Post-op  ----------
## ------------- unadjusted ----------
POSTOP_COMPLICATIONS1 = geeglm(POSTOP_COMPLICATIONS~ PRESENTATION, 
                     data=TEVAR_PROC, family=binomial(link="logit"), 
                     id = CENTERID, corstr = "independence") 

t1 = POSTOP_COMPLICATIONS1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Any Complications Post-op**")%>%as_flex_table()

## ------------- adjusted ----------
POSTOP_COMPLICATIONS2 = geeglm(POSTOP_COMPLICATIONS ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+
                      PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = POSTOP_COMPLICATIONS2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Any Complications Post-op**")%>%as_flex_table()
```




\newpage
## RETX_R_RTOR: Re-intervention

```{r}
## ------------ Re-intervention  ----------
## ------------- unadjusted ----------
RETX_R_RTOR1 = geeglm(RETX_R_RTOR~ PRESENTATION, 
                     data=TEVAR_PROC, family=binomial(link="logit"), 
                     id = CENTERID, corstr = "independence") 
# summary(POSTOP_LOS1)

t1 = RETX_R_RTOR1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Re-intervention**")%>%as_flex_table()

## ------------- adjusted ----------
RETX_R_RTOR2 = geeglm(RETX_R_RTOR ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+
                      PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = RETX_R_RTOR2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Re-intervention**")%>%as_flex_table()
```

\newpage
## BRANCH_POST: Post-treatment Status of All Branches

```{r}
## ------------ Post-treatment Status of All Branches  ----------
## ------------- unadjusted ----------
BRANCH_POST1 = geeglm(BRANCH_POST~ PRESENTATION, 
                     data=TEVAR_PROC, family=binomial(link="logit"), 
                     id = CENTERID, corstr = "independence") 
# summary(POSTOP_LOS1)

t1 = BRANCH_POST1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Post-treatment Status of All Branches**")%>%as_flex_table()

## ------------- adjusted ----------
BRANCH_POST2 = geeglm(BRANCH_POST ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+
                      PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = BRANCH_POST2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Post-treatment Status of All Branches**")%>%as_flex_table()
```

For the following variables, we need to merge age group "<50" and "50-59" so that there's no 0 patients on one level.

```{r}
## ------------- modify dataset ----------
TEVAR_PROC = TEVAR_PROC %>%
  mutate(AGECAT = factor(AGECAT,levels = c('<50','50-59','60-69','70-79','>79'),
                         labels = c('<59','<59','60-69','70-79','>79')))

```


\newpage
## POSTOP_DIALYSIS: Post-op Dialysis

Also account for `OCCLUDED_RENAL`

```{r}
## ------------ Post-op Dialysis  ----------
# table1(~ AGECAT | factor(POSTOP_DIALYSIS),data=subset(TEVAR_PROC, !is.na(POSTOP_DIALYSIS)))

## ------------- unadjusted ----------
POSTOP_DIALYSIS1 = geeglm(POSTOP_DIALYSIS ~ PRESENTATION, 
                                 data=TEVAR_PROC,family=binomial(link="logit"), 
                                 id = CENTERID, corstr = "independence") 

t1 = POSTOP_DIALYSIS1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Post-op Dialysis**")%>%as_flex_table()

## ------------- adjusted ----------
POSTOP_DIALYSIS2 = geeglm(POSTOP_DIALYSIS ~ PRESENTATION+AGECAT+GENDER+
                                   PREOP_SMOKING+PRIOR_AORSURG+PRIOR_CHF+
                                   PREOP_DIALYSIS+PATHOLOGY+extent+
                                   OCCLUDED_RENAL, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = POSTOP_DIALYSIS2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Post-op Dialysis**")%>%as_flex_table()

```

\newpage
## POSTOP_LEGEMBO: Leg Ischemia/Embol

```{r}
## ------------ Leg Ischemia/Emboli  ----------
# table1(~ AGECAT | factor(POSTOP_LEGEMBO),data=subset(TEVAR_PROC, !is.na(POSTOP_LEGEMBO)))
## ------------- unadjusted ----------
POSTOP_LEGEMBO1 = geeglm(POSTOP_LEGEMBO~ PRESENTATION, 
                     data=TEVAR_PROC, family=binomial(link="logit"), 
                     id = CENTERID, corstr = "independence") 
# summary(POSTOP_LOS1)

t1 = POSTOP_LEGEMBO1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Leg Ischemia/Embol**")%>%as_flex_table()

## ------------- adjusted ----------
POSTOP_LEGEMBO2 = geeglm(POSTOP_LEGEMBO ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+
                      PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = POSTOP_LEGEMBO2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Leg Ischemia/Embol**")%>%as_flex_table()
```


\newpage
## POSTOP_RESPIRATORY: Post-op Respiratory

```{r}
## ------------ Post-op Respiratory  ----------
# table1(~ AGECAT | factor(POSTOP_RESPIRATORY),data=subset(TEVAR_PROC, !is.na(POSTOP_RESPIRATORY)))

## ------------- unadjusted ----------
POSTOP_RESPIRATORY1 = geeglm(POSTOP_RESPIRATORY~ PRESENTATION, 
                     data=TEVAR_PROC, family=binomial(link="logit"), 
                     id = CENTERID, corstr = "independence") 

t1 = POSTOP_RESPIRATORY1 %>%
  tbl_regression(exponentiate=TRUE, tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t1),tab_spanner ="**Post-op Respiratory**")%>%as_flex_table()

## ------------- adjusted ----------
POSTOP_RESPIRATORY2 = geeglm(POSTOP_RESPIRATORY ~ PRESENTATION+AGECAT+GENDER+PREOP_SMOKING+
                      PRIOR_AORSURG+PRIOR_CHF+PREOP_DIALYSIS+PATHOLOGY+extent, 
                    family=binomial(link="logit"), data=TEVAR_PROC, 
                    id = CENTERID, corstr = "independence")

t2 = POSTOP_RESPIRATORY2 %>%
  tbl_regression(exponentiate=TRUE,tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2))%>%
  bold_p(t = 0.05)

tbl_merge(tbls = list(t2),tab_spanner ="**Post-op Respiratory**")%>%as_flex_table()
```


\newpage

## Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE,include=TRUE}
```
