---
title: "Survival Analysis for the VQI FBVAR Dataset"
author: "Jennifer Ci, Thu Vu, Lily Hanyi Wang"
output: pdf_document
---

```{r library, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
knitr::opts_chunk$set(fig.width=20, fig.height=20)

library(tidyverse)
library(table1)
library(survival)
library(Hmisc)
library(ggplot2)
library(ggpubr)
library(corrplot)
library(caret)
library(survminer)
library(knitr)
library(kableExtra)
library(gtsummary)
library(flextable)

```

```{r setup wd}
## ------------- working directories for Lily ----------
wd_lily = '/Users/hanyiwang/Desktop/Comparative-analysis-of-treatments-of-CAA'
path_lily = c("../data/FBVAR.csv")


## ------------- working directories for Jenn ----------
# wd_jenn = '/Users/jenn/Desktop/Comparative-analysis-of-treatments-of-CAA'
# path_jenn = c("TEVAR_PROC.csv")

## ------------- working directories for Thu ----------
wd_thu = '/Users/thuvu/Desktop/Comparative-analysis-of-treatments-of-CAA'
path_thu = c("TEVAR_PROC.csv")

## ------------- read data ----------
# setwd(wd_lily)
# FBVAR = read.csv(path_lily)

# setwd(wd_jenn)
# FBVAR = read.csv(path_jenn)

setwd(wd_thu)
TEVAR_PROC1 = read.csv(path_thu)

```


# Cox proportional hazards model for survival analysis

Unadjusted survival curves. Time scale changed from calendar days to calendar years. Used log rank test to produce p-value. Median survival never reached. 

Any changes needed? (e.g, time scale, colors, change to at risk table, add number of censored and/or uncensored events, etc.)

```{r, fig.width=8, fig.height=6}
## Omitting patients with negative survival days
TEVAR_PROC <- subset(TEVAR_PROC1, PROC_SURVIVALDAYS>=0)

## Survival analysis
tte <- TEVAR_PROC %>% with(Surv(PROC_SURVIVALDAYS/365, DEAD))

# compute survival curves
fit <- survfit(tte ~ PRESENTATION, data=TEVAR_PROC)

ggsurv <- ggsurvplot(fit,
           risk.table = TRUE, 
           linetype = "strata",
           surv.median.line = "hv", 
           ggtheme = theme_bw(), 
           xlab = "Time (Year)",
           legend.labs = c("Asymptomatic", "Symptomatic"),
           break.time.by=1)

ggsurv$plot <- ggsurv$plot +
 annotate(
    "text",
    x = 2.5, y = 0.25,
    label = "Unadjusted HR = 2.06 (95% CI: 1.65,2.58) 
    \n Adjusted HR = 1.85 (95% CI: 1.41,2.41)
    \n p < 0.001",
    size = 4
  )

ggsurv

```

Univariate (unadjusted) and Multivariate (adjusted) Cox Proportional Hazards Models. Reference group is asymptomatic patients. 

Variables to adjust for:

- cluster on `CENTERID` 

- `AGECAT`, `GENDER`, `PREOP_SMOKING`, `PRIOR_AORSURG`, `PRIOR_CHF`, `PREOP_DIALYSIS`

- `PATHOLOGY`, `extent`

In the model, we merge groups for the  `extent`: merge "Juxtarenal AAA" with "Type 4 TAAA"; "Type 1 TAAA", "Type 2 TAAA", "Type 3 TAAA", with "Type 5 TAAA". Now `extent` is a binary variable, Juxtarenal or not. 

```{r, fig.pos="H"}
TEVAR_PROC = TEVAR_PROC %>%
  mutate(extent = factor(extent,levels = c("Juxtarenal AAA","Type 1 TAAA","Type 2 TAAA",
                                           "Type 3 TAAA","Type 4 TAAA","Type 5 TAAA"),
                         labels = c('Juxtarenal','No','No','No','Juxtarenal','No')))

# Unadjusted survival model
mod.cox1 <- coxph(tte ~ PRESENTATION, data=TEVAR_PROC)

# Adjusted survival model
mod.cox2 <- coxph(tte ~ PRESENTATION + cluster(CENTERID) + AGECAT + GENDER + 
                    PREOP_SMOKING + PRIOR_AORSURG + PRIOR_CHF + 
                    PREOP_DIALYSIS + PATHOLOGY + extent , 
                  data=TEVAR_PROC)

t1 <- mod.cox1 %>% tbl_regression(exponentiate = TRUE)
t2 <- mod.cox2 %>% tbl_regression(exponentiate = TRUE)

t1 %>% as_flex_table()
t2 %>% as_flex_table()
```

\newpage

## Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE,include=TRUE}
```
