---
title: "Survival Analysis for the VQI FBVAR Dataset"
author: "Jennifer Ci, Thu Vu, Lily Hanyi Wang"
output: pdf_document
---

```{r library, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
knitr::opts_chunk$set(fig.width=20, fig.height=20)

library(tidyverse)
library(survival)
library(survminer)
library(knitr)
library(kableExtra)
library(gtsummary)
library(flextable)

```

```{r setup wd}
## ------------- working directories for Lily ----------
#wd_lily = '/Users/hanyiwang/Desktop/Comparative-analysis-of-treatments-of-CAA'
#path_lily = c("../data/FBVAR.csv")


## ------------- working directories for Jenn ----------
# wd_jenn = '/Users/jennci/Desktop/Comparative-analysis-of-treatments-of-CAA'
# path_jenn = c("TEVAR_PROC.csv")


## ------------- working directories for Thu ----------
wd_thu = '/Users/thuvu/Desktop/Comparative-analysis-of-treatments-of-CAA'
path_thu = c("TEVAR_PROC.csv")
path_thu1 = c("LT 2.csv")

## ------------- read data ----------
# setwd(wd_lily)
# FBVAR = read.csv(path_lily)

# setwd(wd_jenn)
# FBVAR = read.csv(path_jenn)

setwd(wd_thu)
TEVAR_PROC1 = read.csv(path_thu)
LTF = read.csv(path_thu1)

```

# Variables to adjust for

In the unadjusted model, we studied only the differences in the outcomes:

- comparing `PRESENTATION`

In the adjusted models, we also: 

- cluster on `CENTERID` 

- adjust for `AGECAT`, `GENDER`, `PREOP_SMOKING`, `PRIOR_AORSURG`, `PRIOR_CHF`, `PREOP_DIALYSIS`

- adjust for `PATHOLOGY`, `extent`

- primary outcome: All-cause mortality 

- secondary outcome: Time-to-first reintervention for patients with long-term follow-up 

For the outcomes described below, Kaplan-Meier curves were produced grouped by presentation, asymptomatic and symptomatic. 

For the primary outcome only, we fitted a univariate Cox proportional hazards model and a multivariate stratified Cox proportional hazards model stratifying on sex.

*To fit the models, we merge groups for the  `extent`: merge "Juxtarenal AAA" with "Type 4 TAAA"; "Type 1 TAAA", "Type 2 TAAA", "Type 3 TAAA", with "Type 5 TAAA". Now `extent` is a binary variable, Juxtarenal or not.*

# Primary Outcome: All-Cause Mortality 

```{r, fig.width=8, fig.height=6}
### Primary Outcome: All-Cause Mortality 
# omitting patients with negative survival days
TEVAR_PROC <- subset(TEVAR_PROC1, PROC_SURVIVALDAYS>=0)

# create survival object, time-to-event
# converted days to years 
tte <- TEVAR_PROC %>% with(Surv(PROC_SURVIVALDAYS/365, DEAD))

# compute survival curves
fit <- survfit(tte ~ PRESENTATION, data=TEVAR_PROC)

# plotting KM curves
ggsurv <- ggsurvplot(fit,
           risk.table = TRUE, 
           linetype = "strata",
           surv.median.line = "hv", 
           ggtheme = theme_bw(), 
           xlab = "Time (in years)",
           legend.labs = c("Asymptomatic", "Symptomatic"),
           break.time.by=1, 
           caption="HR = Hazard Ratio, CI = Confidence Interval")

ggsurv$plot <- ggsurv$plot +
 annotate(
    "text",
    x = 2.5, y = 0.25,
    label = "Unadjusted HR = 2.06 (95% CI: 1.65,2.58) 
    \n Adjusted HR = 1.84 (95% CI: 1.41,2.41)
    \n p < 0.001",
    size = 4
  )

ggsurv

```

Due to violating the proportional-hazards assumption, the multivariate Cox proportional-hazards model was stratified on sex to resolve this issue. 

```{r, fig.pos="H"}
# changing extent into a binary variable
TEVAR_PROC = TEVAR_PROC %>%
  mutate(extent = factor(extent,levels = c("Juxtarenal AAA","Type 1 TAAA","Type 2 TAAA",
                                           "Type 3 TAAA","Type 4 TAAA","Type 5 TAAA"),
                         labels = c('Juxtarenal','No','No','No','Juxtarenal','No')))

# Unadjusted survival model
mod.cox1 <- coxph(tte ~ PRESENTATION, data=TEVAR_PROC)

# Adjusted survival model
mod.cox2 <- coxph(tte ~ PRESENTATION + cluster(CENTERID) + AGECAT + strata(GENDER) + 
                    PREOP_SMOKING + PRIOR_AORSURG + PRIOR_CHF + 
                    PREOP_DIALYSIS + PATHOLOGY + extent , 
                  data=TEVAR_PROC)

t1 <- mod.cox1 %>% 
  tbl_regression(exponentiate = TRUE, 
                 tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2)) %>%
  bold_p(t = 0.05)
tbl_merge(tbls = list(t1),tab_spanner ="**All-Cause Mortality**") %>% 
  as_flex_table()

t2 <- mod.cox2 %>% 
  tbl_regression(exponentiate = TRUE, 
                 tidy_fun = broom.mixed::tidy,
                 pvalue_fun = function(x) style_pvalue(x, digits = 2)) %>%
  bold_p(t = 0.05)
tbl_merge(tbls = list(t2),tab_spanner ="**All-Cause Mortality**") %>% 
  as_flex_table()

```

\newpage

# Secondary Outcome: Long-term Follow-up First Reintervention (time-to-event outcome)

```{r, fig.width=8, fig.height=6}
### Secondary Outcome: Long-term Follow-up First Reintervention 
### (time-to-event outcome)
# filtering the LTF dataset to only include FEVAR procedures
t <- as.data.frame(table(TEVAR_PROC1$PRIMPROCID))
LTF_merge <- LTF[LTF$PRIMPROCID %in% t$Var1,]

# replacing all missing in number of reinterventions with 0
LTF_merge$total_reint[is.na(LTF_merge$total_reint)] <- 0

# creating event variable, binary re-intervention
# 1 = had at least 1 reintervention, 0 = had 0 reinterventions
LTF_merge$retx_bin <- ifelse(LTF_merge$total_reint>=1, 1, 0)
# creating time variable (in days)
LTF_merge$time <- ifelse(LTF_merge$retx_bin==1, 
                         LTF_merge$first_reint_time, LTF_merge$new_surv)

# omitting patients with negative survival days
LTF_merge <- subset(LTF_merge, time>=0)

# merging proc and ltf datasets on procedure ID
LTF_comb <- merge(LTF_merge, TEVAR_PROC1, by = "PRIMPROCID")

# create survival object, time-to-event
# converted days to years 
tte1 <- LTF_comb %>% with(Surv(time/365, retx_bin))

# compute survival curves
fit1 <- survfit(tte1~PRESENTATION, data=LTF_comb)

# plotting KM curves
ggsurvplot(
  fit1,
  pval = TRUE,
  risk.table = TRUE,
  linetype = "strata",
  ggtheme = theme_bw(),
  legend.labs = c("Asymptomatic", "Symptomatic"),
  xlab = "Time (in years)",
  ylab = "Non-reintervention probability",
  break.time.by = 1,
  xlim = c(0,5),
  caption = "HR = Hazard Ratio, CI = Confidence Interval"
)

```

\newpage

## Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE,include=TRUE}
```
